---
title: "Results"
date: last-modified
number-sections: true
toc: true
toc-depth: 4
format:
  html:
    embed-resources: true
---

```{r}
#| echo: false
library(coda)
```


## Checking convergence and WAIC models

```{r}
#| echo: false

# WAIC can be used even when we have different observation models: https://discourse.mc-stan.org/t/can-waic-looic-be-used-to-compare-models-with-different-likelihoods/7380

Path <- "../data/posterior_samples"
files <- dir(path = Path)
files <- files[substring(files, 1, 3) != "pos"]
for(fil in files){
  cat("\n **", fil, "**\n")
  load(paste0("../data/posterior_samples/", fil))
  print(unlist(settings))
  print(gelman.diag(out$samples))
  print(out$WAIC)
}
```

The upper CI of the 'potential scale reduction factor' by Gelman and Rubin is a bit high for some models, so we should probably either run these models longer or do something to get better mixing.

Assuming that this convergence issue will not affect the WIAC-ranking of the models, the best model is 'gamma_2' (this model has pretty good convergence criteria, but we can run for longer to get even better).

## Posterior predictive checks of best model

### Bayesian p-value based on Y

```{r}
#| echo: false
samp <- as.matrix(out$samples)
plot(samp[,"Disc_New_Y"] ~ samp[,"Disc_Y"])
abline(0, 1, col="red")
mean(samp[, "Disc_New_Y"] > samp[, "Disc_Y"])
```

### Bayesian p-value based on y

```{r}
#| echo: false

plot(samp[,"Disc_New_y"] ~ samp[,"Disc_y"])
abline(0, 1, col="red")
mean(samp[, "Disc_New_y"] > samp[, "Disc_y"])
```

### Conclusion

No indication of serious lack of fit.

## Summary of best model

```{r}
#| echo: false
load("../data/posterior_samples/gamma_2.RData") # Best model
summary(out$samples)
```

## Predictions from the best model

```{r}
#| echo: false
#| warning: FALSE

library(ggplot2)
library(hrbrthemes) 
library(cowplot)

source("pred_plot_functions.r")

#############
# Preparing #
#############

load(file = "../data/UseData.rda")
load(file = "../data/Counts.rda")

sam_names <- c("Haugen (April)", "Haugen (March)", "Raa (April)", "Raa (March)", "Soere Bjoerkum (April)", "Soere Bjoerkum (March)", "Sprakehaug (April)", "Sprakehaug (March)")

predictor_variable <- UseData$mean_field_dist
Xlab <- "Distance from field (m)"
Ylab <- expression(Density~of~deer~(km^-2))

post_samp_mat <- as.matrix(out$samples)

X <- seq(0, max(predictor_variable, na.rm = TRUE), length.out=50)
X_mean <-  mean(predictor_variable, na.rm=TRUE)
X_sd <- sd(predictor_variable, na.rm=TRUE)
X_st <- (X - X_mean)/X_sd

mpv <- mean(predictor_variable, na.rm = TRUE) # mean predictor variable
#pap <- mean(post_samp_mat[,"x_at_peak"])*X_sd + X_mean # predictor variable at peak

############
# Plotting #
############

plots <- pred_plots()

plot_grid(plots[[1]],
          plots[[2]],
          plots[[3]],
          plots[[4]])
plot_grid(plots[[5]],
          plots[[6]],
          plots[[7]],
          plots[[8]])
```
